The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-06 analysis/paper/paper.qmd
Add dependencies between code chunks
Add line breaks

@@

```{r clean-text}
#| echo: false

@@

```{r}
#| label: ngrams

@@

bigram_counts
bigram_stem_counts

## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text")

>>>>

Description of text extraction; raw data available on 4TU.ResearchData at...

@@

```{r clean-text}
#| echo: false
#| dependson: get-pdf-text

@@

```{r}
#| label: ngrams
#| dependson: clean-text

@@

bigram_counts
bigram_stem_counts
```

```{r}
## Trigrams
emu_trigrams <- emu |> 
  get_ngrams(n = 3, title_col = "title", text_col = "text")
